### 2019-01-12 Metrics1.tex
Metrics1

\textbf{Solution}
\begin{enumerate}[a.]
	\item 
	\begin{align*}
	\expect[\sqrt{x}] = \int_{0}^1 \sqrt{x}dx = \frac{2}{3}\\
	\expect[u] = \expect[\expect[u|X]] = \expect[0] = 0\\
	\expect[y] = \frac{2}{3} + 0 = \frac{2}{3}
	\end{align*}
	\item
	\begin{align*}
	\expect[\hat{\beta_1}|x_1, \dots, x_n] = \expect \left[\frac{\sum_{i=1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i=1}^n (x_i - \bar{x})^2}\bigg|x_1, \dots, x_n\right] =\\
	= \expect \left[\frac{\sum_{i=1}^n (x_i - \bar{x})(\sqrt{x_i} + u_i - \overline{\sqrt{x}} -  \bar{u})}{\sum_{i=1}^n (x_i - \bar{x})^2}\bigg|x_1, \dots, x_n\right]
	\end{align*}
	\end{enumerate}
\end{document}

>>>>

\textbf{Solution}
\begin{enumerate}[a.]
	\item 
	\begin{align*}
	\expect[\sqrt{x}] = \int_{0}^1 \sqrt{x}dx = \frac{2}{3}\\
	\expect[u] = \expect[\expect[u|X]] = \expect[0] = 0\\
	\expect[y] = \frac{2}{3} + 0 = \frac{2}{3}
	\end{align*}
	\item Denote $\overline{\sqrt{x}} = \frac{1}{n}\sum_{i=1}^n \sqrt{x_i}$, then
	\begin{align*}
	\expect[\hat{\beta_1}|x_1, \dots, x_n] = \expect \left[\frac{\sum_{i=1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i=1}^n (x_i - \bar{x})^2}\bigg|x_1, \dots, x_n\right] =\\
	= \expect \left[\frac{\sum_{i=1}^n (x_i - \bar{x})(\sqrt{x_i} + u_i - \overline{\sqrt{x}} -  \bar{u})}{\sum_{i=1}^n (x_i - \bar{x})^2}\bigg|x_1, \dots, x_n\right]
	\end{align*}
	Since
	\begin{align*}
	\expect \left[ \sum_{i=1}^n (x_i - \bar{x})(u_i - \bar{u})\bigg|x_1, \dots, x_n\right] = \expect \left[\sum_{i=1}^n (x_i - \bar{x})u_i\bigg|x_1, \dots, x_n\right]
	\end{align*}
	assuming independence of the sample, for each $i$
	\begin{align*}
	\expect[(x_i - \bar{x})u_i|x_1, \dots, x_n] = \expect[(x_i - \bar{x})u_i|x_i] = 0
	\end{align*}
	Thus, 
	\begin{align*}
	\expect[\hat{\beta_1}|x_1, \dots, x_n] = \frac{\sum_{i=1}^n (x_i - \bar{x})(\sqrt{x_i} - \overline{\sqrt{x}})}{\sum_{i=1}^n (x_i - \bar{x})^2}
	\end{align*}
	Similarly,
	\begin{align*}
	\expect[\hat{\beta_0}|x_1, \dots, x_n] = \expect[\bar{y} - \hat{\beta_1}\bar{x}|x_1, \dots, x_n] = \expect[\overline{\sqrt{x}} + \bar{u} - \hat{\beta_1}\bar{x}|x_1, \dots, x_n] = \\
	=\overline{\sqrt{x}} + \expect[\bar{u}|x_1, \dots, x_n] - \bar{x}\expect[\hat{\beta_1}|x_1, \dots, x_n] = \overline{\sqrt{x}} - \bar{x} \cdot \frac{\sum_{i=1}^n (x_i - \bar{x})(\sqrt{x_i} - \overline{\sqrt{x}})}{\sum_{i=1}^n (x_i - \bar{x})^2}
	\end{align*}
	\end{enumerate}
\section*{Problem 5}
 Using R, compute the sample mean and standard deviation of \textit{ahe} (average hourly earnings),
\textit{yrseduc} (years of education), and \textit{female}.

\begin{align*}
\text{mean(ahe)} = 15.19042\\
\text{sd(ahe)} = 8.027257\\
\text{mean(yrseduc)} = 13.46549\\
\text{sd(yrseduc)} = 2.479692\\
\text{mean(female)} = 0.4385083\\
\text{sd(female)} = 0.49627
\end{align*}
\section*{Problem 6}
 Estimate a regression of \textit{ahe} on \textit{yrseduc}.
 \begin{enumerate}
 	\item What is the coefficient on \textit{yrseduc}? Explain in words what it means. Is the numerical
value of your estimate large or small in an economic (real-world) sense?
\item Graph the data points and the estimated regression line.
\item Is the slope coefficient statistically significantly different from zero? Show how you reach
this conclusion. Use heteroskedasticity-robust standard errors to answer this question.
\item Report the 95\% confidence interval for $\beta_1$, the slope of the population regression line.
Use heteroskedasticity-robust standard errors to answer this question.
\item  What is the $R^2$ of this regression? What does this mean?
\item  Compute the correlation coefficient between ahe and yrseduc, and compare its square to
the $R^2$. How are the correlation coefficient and the $R^2$
related?
\item What is the root mean squared error of the regression? What does this mean?
\item Based on your graph from (b), does the error term appear to be homoskedastic or
heteroskedastic?

\end{enumerate}

\textbf{Solution}
\begin{enumerate}
	\item Coefficient on \textit{yrseduc} is 1.32186. That means that on each additional years of education the average size of the per-hour salary increases by 1.32186 dollars/hour.
	\item \begin{figure}[h]
		\centering
		\includegraphics[width=0.7\textwidth]{Rplot}
		\caption{Regression line and data points}
	\end{figure}
\end{enumerate}
\end{document}
